%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=RoyalBlue, linkcolor=RoyalBlue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\LARGE \scshape Anish Reddy} \\ \vspace{3pt}
    \footnotesize 437-557-2209 $|$ \href{mailto:anishreddy3456@gmail.com}{anishreddy3456@gmail.com} $|$ 
    \href{https://linkedin.com/in/anishreddyk}{linkedin.com/in/anishreddyk} $|$
    \href{https://github.com/Anish-Reddy-K}{github.com/Anish-Reddy-K} $|$
    \href{https://arkr.ca}{arkr.ca} $|$
    Waterloo, Canada
\end{center}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: Python, C/C++, SQL (BigQuery, Postgres), FastAPI, TypeScript, React, Next.js} \\
     \textbf{AI Engineering}{: RAG, AI Agents, Multi-Agent Systems, LangChain, LangGraph, MCP, Tool Calling, LLM Evaluation} \\
     \textbf{ML \& Evaluation}{: PyTorch, Hugging Face Transformers, Scikit-learn, MLflow, Model Evaluation, OpenCV, NumPy} \\
     \textbf{Cloud, Data \& Systems}{: GCP, Vertex AI, Azure, Docker, Airflow, Redis, Clourflare, Pinecone, pgvector}
    }}
 \end{itemize}

% See skill-bank.txt for targeted ATS swaps.


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Engineer Intern}{May 2025 -- Present}
      {Geotab}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Engineered a production Data Quality Assistant with a root-cause agent that traces BigQuery, Airflow, metadata, data contracts, and code paths, isolates upstream breakpoints, and converts failed checks into owner-ready remediation guidance.}
        \resumeItem{Rewrote data lineage across a petabyte-scale ecosystem, improving accuracy from $\sim$90\% to near-100\% for data traceability.}
        \resumeItem{Implemented anomaly and schema-drift detectors for critical data assets, catching silent failures before downstream impact.}
        \resumeItem{Built proactive alerting that notifies data owners of detected anomalies and changes, enabling faster issue resolution.}
      \resumeItemListEnd
      \vspace{6pt}
      
    \resumeSubheading
      {AI Engineer Intern}{Jan 2025 -- Apr 2025}
      {Brisk AI}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Engineered role-based agents for Brisk's agentic AI suite, automating operational workflows across enterprise teams.}
        \resumeItem{Integrated agents with enterprise systems and internal tools, enabling context-aware actions beyond static chat responses.}
        \resumeItem{Built a field troubleshooting agent that diagnoses on-site issues, guides technicians, and captures expert workflows.}
      \resumeItemListEnd
      \vspace{6pt}

    \resumeSubheading
      {AI/ML Engineer Intern}{May 2024 -- Apr 2025}
      {OCAS}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Built and launched \href{https://advisor.beta.ontariocolleges.ca/}{AI Advisor}, a RAG chatbot used by 1,000+ high schoolers to match interests to college programs.}
        \resumeItem{Built a resume parser extracting skills, education, and career signals to personalize Ontario college recommendations.}
        \resumeItem{Deployed AI Advisor on Azure with vector search, guardrails, and monitoring for reliable student-facing recommendations.}
      \resumeItemListEnd
      \vspace{6pt}

    \resumeSubheading
      {AI/ML Research Intern}{Sep 2023 -- Apr 2024}
      {SMART Centre}{Waterloo, ON}
      \resumeItemListStart
        \resumeItem{Optimized small language models for edge devices, reducing memory and compute under tight embedded constraints.}
        \resumeItem{Deployed speech-to-text models on embedded systems, reducing latency while preserving transcription quality.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Notable Projects \& Startups \hfill \normalfont\small\href{https://arkr.ca/projects}{View All Projects}}
    \resumeSubHeadingListStart
	      \resumeProjectHeading
	          {\href{https://identpix.com}{\textbf{Identipix}} $|$ \emph{Founder - AI photo delivery and lead-gen platform for photographers and studios} $|$ \href{https://identpix.com}{Technical Overview}}{}
	          \resumeItemListStart
	            \resumeItem{Built an AI photo delivery platform that matches guest selfies to event images to generate private galleries and studio leads.}
	          \resumeItemListEnd
	      \resumeProjectHeading
	          {\textbf{Aqua Pinion} $|$ \emph{Drowning Detection and Prevention Chest Strap}}{}
	          \resumeItemListStart
	            \resumeItem{Engineered a sensor-driven wearable using ML to detect drowning with 95\%+ precision and deploy a life-saving inflatable.}
	          \resumeItemListEnd
	      \resumeProjectHeading
	          {\href{https://hubrix.ca}{\textbf{Hubrix}} $|$ \emph{Co-Founder, Modular LED Wall Dashboard}}{}
	          \resumeItemListStart
	            \resumeItem{Built a modular LED wall made of tiles that snap into any shape and turns live data into ambient, glanceable dashboards.}
	          \resumeItemListEnd
	      \resumeProjectHeading
	          {\href{https://github.com/Anish-Reddy-K/diagrammer.git}{\textbf{Diagrammer}} $|$ \emph{Python diagram renderer, Claude Code/Codex Skill, MCP Server}}{}
	          \resumeItemListStart
	            \resumeItem{Built an AI agent-native renderer that turns JSON specs into clean SVG diagrams for docs, blogs, PRs, and slides.}
	          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------ACTIVITIES-----------
\section{Activities \& Leadership}
    \resumeSubHeadingListStart
        \item\small{
            \textbf{Founder \& Lead Organizer} $|$ \emph{\href{https://conhacks.io}{\textbf{ConHacks}}} -- Founded and led 3 hackathon iterations, scaling to 200+ participants in 3 years. \vspace{-2pt}
        }
        \item\small{
            Secured 600+ registrations, 200+ attendees and 15+ sponsors for ConHacks 2026, executed end-to-end by a lean 3 member team. \vspace{-2pt}
        }
        \item\small{
            \textbf{Co-Founder \& President} $|$ \emph{\href{https://conestogacomputingsociety.com}{\textbf{Conestoga Computing Society}}} -- Founded a 300-member CS community; hosted multiple events. \vspace{-2pt}
        }
        \item\small{
            \textbf{Executive Lead (Former)} $|$ \emph{Google Developers Group - On Campus} -- Organized workshops, speaker series, and other events. \vspace{-2pt}
        }
        \item\small{
            \textbf{Student Lead (Former)} $|$ \emph{ATAL Tinkering Labs} -- Helped 100+ students with projects, winning Student Innovator of the Year. \vspace{-2pt}
        }
        \item\small{
            \textbf{Leader \& Tutor (Former)} $|$ \emph{Peer-Assisted Learning} -- Tutored $\sim$20 students in C \& DSA, improving grades by 50\% on average. \vspace{-2pt}
        }
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Science (Honours)}{Sep 2026 (Expected)}
      {Conestoga College, Waterloo}{}
  \resumeSubHeadingListEnd


%-----------AWARDS-----------
\section{Awards \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Awards}{: HackThe6ix (Best Beginner Hack), NIRD RISC (Gold Medal), FGSI (Gold Medal), CSI Student Service Award} \\
     \textbf{Community}{: Mentor (Hack The North, Hawk Hacks), Judge (GDSC Hacks, ConHacks), Speaker (GDG, Queen's University)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
